An algorithm for finding the global extremum of a partially defined function\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-08-28 2023/MMST/samplepaper.tex
one more reference

From our experience in solving the applied optimization problems [refs??], we will assume the total volume of the non-computability regions to be a small fraction of the whole volume of the search domain $D$ (about 10-20\%)\footnote{When testing the algorithm, we have considered also more complex problem statements, which the volume of the non-computability region achieved 50-80\% in. The problems of this kind were solved by the algorithm proposed successfully as well but a large number of trials was required to solve the problem because the method attempted to explore the whole non-computability region. In this connection, in the rules of constructing the problems the experiments for the dimensionality $N=5$ were modified so that the non-computability region were located in the corners of the search domain only.}.

>>>>

From our experience in solving the applied optimization problems \cite{Barkalov2022,Gubaydullin2022}, we will assume the total volume of the non-computability regions to be a small fraction of the whole volume of the search domain $D$ (about 10-20\%)\footnote{When testing the algorithm, we have considered also more complex problem statements, which the volume of the non-computability region achieved 50-80\% in. The problems of this kind were solved by the algorithm proposed successfully as well but a large number of trials was required to solve the problem because the method attempted to explore the whole non-computability region. In this connection, in the rules of constructing the problems the experiments for the dimensionality $N=5$ were modified so that the non-computability region were located in the corners of the search domain only.}.
